Coherent Hyper-Raman Four Wave Mixing Spectroscopies

### 2024-06-11 paper.tex
small edits

\documentclass[aip, jcp, reprint, twocolumn]{revtex4-2}

@@

\begin{abstract}
Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics.
Three wave mixing vibrational spectroscopies are similarly often used to understand the spectroscopy and dynamics of interfacial species.
Most of these methods rely on infrared or Raman transitions to generate output. 
The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques.
Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
We derive selection rules and coherent interference effects in singly resonant SIVE (SR-SIVE).
The theory of SR-SIVE is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant SIVE (DR-SIVE), akin to a resonant hyper-Raman process. 
DR-SIVE is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
The linenarrowing abilities of DR-SIVE are discussed.
We showcase the difference in selection rules of SR-SIVE and DR-SIVE through a study of cyanocobalamin, highlighting the sensitivity of these measurements on non-resonant and resonant hyper-Raman hyperpolarizabilities, respectively.
\end{abstract}

@@

\section{Experimental Methods}
The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG "DF2", Light Conversion).
OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
Grating and BBO crystal positions in OPA2 were computer controlled through communication with 50 mm DC actuators (PMC). %todo: who tf makes PMC motors?
The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
The power spectra and tuning results are found in Figure X.%todo: actually graph these
Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
The beams are focused into the sample using a BOXCARS geometry.\cite{RN308, Kaufman2024}
To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/wmel1.png}
	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant SR-SIVE pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries. \cite{RN286, RN352}
	$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
	Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
	These diagrams can be permuted to generate additional resonant WMEL diagrams.}
	\label{fig:sivewmel}
\end{figure}

@@

\subsection{Rovibrational SR-SIVE Selection Rules} %this can probably be deleted but wanted to add just in case...
Recent developments in nonlinear spectroscopy have demonstrated the feasibility of multidimensional infrared spectroscopy of gaseous and quasi-free species. \cite{Ziegler2018, Gronborg2022, RN325, Chen2024}
DOVE and 2D-IR have been used to isolate coupling between fundamentals, overtones and combination bands of gaseous species in several molecular systems. 
Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy,\cite{RN515} we briefly investigate the properties of rovibrational SR-SIVE.

The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} through the Wigner-Eckart theorem. \cite{Kowzan2022}
It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in \{-1, 0 ,1\}$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Andrews1990}
%there is some fancy way to note that theres no index constraint but i dont remember the language...
As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$ transitions are allowed, i.e., SIVE-IR features arise only from P or R branches (assuming the ground state is $\ket{g00}$).
This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.

\subsection{Quantitative SR-SIVE}
With the selection rules of SR-SIVE understood for vibrational and rovibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.

Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}}$ and $\Im{\chi^{(3)}}$.\cite{Levenson1974_1, Levenson1974_2}
Resonant SIVE lineshapes are complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra. \cite{RN418}

@@

The SIVE $\chi^{(3)}_{IJKL}$ expresson is
\begin{equation}\label{chi3}
\begin{split}
		\chi^{(3)}_{IJKL} &\sim \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
\end{split}
\end{equation}
The steps behind orientational averaging of $\gamma_{ijkl}$ are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
Orientational averaging for specific input polarizations shows that specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
Infrared spectra can provide values for different $\vec{\mu}$ components.
Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$. \cite{RN459}
Neglecting rotational dependence, $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$.
Substituting into \autoref{chi3} shows that
\begin{subequations}
	\begin{equation}
		\begin{split}
			\chi^{(3)}_{IJKL} &\sim \langle \beta_{ijk} \mu_l \rangle\\
			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
		\end{split}
	\end{equation}
This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
Continuing, we see
	\begin{equation}
		\langle \beta_{ijk} \rangle \sim \frac{\sqrt{3}}{\mu} \chi^{(3)}_{IJKL}
	\end{equation}
\end{subequations}
Since $\mu^2$ can be extracted by fitting infrared spectra,\cite{RN412} it is clear that different polarization schemes in SIVE spectroscopy give a measurement of $\beta_{ijk}$ values.
SIVE can therefore provide useful insight into the sensitivity of hyper-Raman spectroscopy to different infrared active vibrations.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/wmel2.png}
	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering SR-SIVE pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
	(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.}
	\label{fig:sivewmel2}
\end{figure}
\begin{widetext}
We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
The third order response functions, $R^{(3)}$, for SR-SIVE-IR-II ($R^{(3)}_{S_{II}}$) and SR-SIVE-Raman ($R^{(3)}_{R}$) (\autoref{fig:sivewmel2}a, b) are 
\begin{subequations}
	\begin{equation} \label{mixing:a}
		R^{(3)}_{S_{II}} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)
	\end{equation}
	\begin{equation}\label{mixing:b}
		\begin{split}
			R^{(3)}_{R} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2) = - R^{(3)}_{S_{II}} (t_2)\\
		\end{split}
	\end{equation}
\end{subequations}
By assuming that the beams which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
	\begin{equation}\label{polarization_SRSIVE_a}
		\begin{split}
			\vec{P}^{(3)}(t) &= \vec{P}_{S_{II}}(t) + \vec{P}_{R}(t)\\
			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) + R^{(3)}_{R} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau)\\
			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) - R^{(3)}_{S_{II}} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau) \\
			&= 0
		\end{split}
	\end{equation}
It is clear the total output polarization for SR-SIVE-IR-II and SR-SIVE-Raman vanishes, or, SR-SIVE-IR-II and SR-SIVE-Raman perfectly destructively interfere.
\end{widetext}
The absence of SR-SIVE-IR-II pathways in ultrafast DOVE work is rationalized by this calculation. \cite{RN367, McDonnell2024}
In the case of the time ordered SR-SIVE-IR-I pathway, there are no opportunities for interference as all other pathways are nonresonant with the first interaction. 
A possible mechanism for interfering output in the SR-SIVE-I pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{Zhu87} so cascades are unlikely to inhibit output in centrosymmetric media.
In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important. 
Generally, for nonlinear spectroscopies which share the same phasematching conditions as SR-SIVE (e.g., DOVE), it is useful to note that SR-SIVE-IR-I is not canceled, whereas SR-SIVE-IR-II and SR-SIVE-Raman permanently cancel.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/wmel3.png}
	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs. $\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
	\label{fig:doubsive}
\end{figure}

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{main/cob.png}
	\caption{
		(a,c) Singly Resonant SIVE (SR-SIVE) and (b,d) Doubly Resonant SIVE (DR-SIVE) response of CNCbl using the $-\vec{k}_1 + 2\vec{k}_2$ and $\vec{k}_1 + 2\vec{k}_2$ phasematching geometries, respectively.
		Here, $\omega_2 = 8000$ cm$^{-1}$.
		$\omega_1$ is stepped in 10 $^{-1}$ intervals.
		The spectra are smoothed and power-normalized for frequency dependent power fluctuations during the scan.
		Gray pixels indicate spectral noise.
		The blue trace in (a), (b) corresponds to the spectrum at $\tau_{12}$ = 0 in (c,d), respectively.
		The red trace is an FT-IR spectrum of CNCbl, sourced from NIST. 
		All spectra are normalized to their most intense feature on $\omega \in [1300, 1700]$ cm$^{-1}$.}
	\label{fig:cobsive}
\end{figure*}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/corr_contour.png}
	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
	\label{fig:contours}
\end{figure}

>>>>

\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}

@@

\begin{abstract}
Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics.
Three wave mixing vibrational spectroscopies are similarly used to understand the spectroscopy and dynamics of interfacial species.
Most of these methods rely on infrared or Raman transitions to generate output. 
The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques to understand the spectroscopy and dynamics of isotropic systems.
Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
We derive selection rules and coherent interference effects in singly resonant SIVE (SR-SIVE).
The theory of SR-SIVE is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant SIVE (DR-SIVE), akin to a resonant hyper-Raman process. 
DR-SIVE is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
The linenarrowing abilities of DR-SIVE are discussed.
We showcase the difference in selection rules of SR-SIVE and DR-SIVE through a study of cyanocobalamin, highlighting the sensitivity of these measurements on non-resonant and resonant hyper-Raman hyperpolarizabilities, respectively.
\end{abstract}

@@

\section{Experimental Methods}
The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG "DF2", Light Conversion).
OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
Grating and BBO crystal positions in OPA2 were computer controlled through communication with 50 mm DC actuators (PMC). %todo: who tf makes PMC motors?
The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
The power spectra and tuning results are found in Figure X.%todo: actually graph these
Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
The beams are focused into the sample using a BOXCARS geometry.\cite{RN308, Kaufman2024}
To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.
All spectra are reported on the intensity scale. %@dan if we should change to amp lmk

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{wmel1.png}
	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant SR-SIVE pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries. \cite{RN286, RN352}
	$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
	Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
	These diagrams can be permuted to generate additional resonant WMEL diagrams.}
	\label{fig:sivewmel}
\end{figure}

@@

\subsection{Rovibrational SR-SIVE Selection Rules} %this can probably be deleted but wanted to add just in case...
Recent developments in nonlinear spectroscopy have demonstrated the feasibility of multidimensional infrared spectroscopy of gaseous and quasi-free species. \cite{Ziegler2018, Gronborg2022, RN325, Chen2024}
DOVE and 2D-IR have been used to isolate coupling between fundamentals, overtones and combination bands of gaseous species in several molecular systems. 
Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy,\cite{RN515} we briefly investigate the properties of rovibrational SR-SIVE.
In the discussion that follows, to avoid integration over velocity dependent distributions, we assume the experiment is performed at 0 K.
The velocity dependence of output density matrix elements does not manipulate quantum mechanical selection rules. \cite{Bracamonte2003}

The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the total angular momentum and $M$ is its projection onto the space fixed quantization axis).
By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, the matrix elements in \autoref{sivebeta} can be evaluated through the Wigner-Eckart theorem.
It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.\cite{Andrews1978}
Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in \{-1, 0 ,1\}$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Andrews1990}
%there is some fancy way to note that theres no index constraint but i dont remember the language...
As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$ transitions are allowed, i.e., SIVE-IR features arise only from P or R branches (assuming the ground state is $\ket{g00}$).
This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.

\subsection{Quantitative SR-SIVE}
With the selection rules of SR-SIVE understood for vibrational and rovibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.
Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}}$ and $\Im{\chi^{(3)}}$.\cite{Levenson1974_1, Levenson1974_2}
In previous studies, following the method introduced by Levenson and Bloembergen, an internal standard was added to the sample.
The internal standard in most experiments was chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation). \cite{Levenson1974_2, RN351, RN345}
Interference between the sample and internal standard resonances allowed measurment of $\chi^{(3)}$.
Such a method does not require measurment of absolute intensities and instead relies on self-heterodyning of the internal standard signal. 
Resonant SIVE lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra. \cite{RN418}

@@

The SIVE $\chi^{(3)}_{IJKL}$ expresson is
\begin{equation}\label{chi3}
\begin{split}
		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
\end{split}
\end{equation}
The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
Infrared spectra can provide values for different $\vec{\mu}$ components.
Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$. \cite{RN459}
Neglecting rotational dependence, $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$.
Substituting into \autoref{chi3} shows that
\begin{subequations}
	\begin{equation}
		\begin{split}
			\langle \gamma_{ijkl} \rangle &\sim \langle \beta_{ijk} \mu_l \rangle\\
			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
		\end{split}
	\end{equation}
This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
Continuing by substituting in the results found in \autoref{SIVEselection}, we see
	\begin{equation}
		\langle \beta_{ijk} \rangle = - 24\sqrt{3} \frac{\hbar \varepsilon_0 \Delta_{gv}}{NF(\omega_4)\rho_{gg}} \frac{\chi^{(3)}_{IJKL}}{\mu}
	\end{equation}
\end{subequations}
Since $\mu^2$ can be extracted by fitting infrared spectra,\cite{RN412} it is clear that different polarization schemes in SIVE spectroscopy give a measurement of $\beta_{ijk}$ values.
SIVE can therefore provide useful insight into the sensitivity of hyper-Raman spectroscopy to different infrared active vibrations.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{wmel2.png}
	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering SR-SIVE pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
	(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a coherent anti-Stokes Raman (CARS)-type process.}
	\label{fig:sivewmel2}
\end{figure}
\begin{widetext}
We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
The third order response functions, $R^{(3)}$, for SR-SIVE-IR-II ($R^{(3)}_{S_{II}}$) and SR-SIVE-Raman ($R^{(3)}_{R}$) (\autoref{fig:sivewmel2}a, b), suppressing tensor indices, are 
\begin{subequations}
	\begin{equation} \label{mixing:a}
		R^{(3)}_{S_{II}} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)
	\end{equation}
	\begin{equation}\label{mixing:b}
		\begin{split}
			R^{(3)}_{R} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2) = - R^{(3)}_{S_{II}} (t_2)\\
		\end{split}
	\end{equation}
\end{subequations}
By assuming that the fields which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
	\begin{equation}\label{polarization_SRSIVE_a}
		\begin{split}
			\vec{P}^{(3)}(t) &= \vec{P}_{S_{II}}(t) + \vec{P}_{R}(t)\\
			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) + R^{(3)}_{R} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau)\\
			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) - R^{(3)}_{S_{II}} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau) \\
			&= 0
		\end{split}
	\end{equation}
It is clear the total output polarization for SR-SIVE-IR-II and SR-SIVE-Raman vanishes, or, SR-SIVE-IR-II and SR-SIVE-Raman perfectly destructively interfere.
\end{widetext}
The absence of SR-SIVE-IR-II pathways in ultrafast DOVE work is rationalized by this calculation. \cite{RN367, McDonnell2024}
In the case of the time ordered SR-SIVE-IR-I pathway, there are no opportunities for interference as all other pathways are nonresonant with the first interaction. 
A possible mechanism for interfering output in the SR-SIVE-I pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{Zhu87} so cascades are unlikely to inhibit output in centrosymmetric media.
In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important. 
Generally, for nonlinear spectroscopies which share the same phasematching conditions as SR-SIVE (e.g., DOVE), it is useful to note that SR-SIVE-IR-I is not canceled, whereas SR-SIVE-IR-II and SR-SIVE-Raman permanently cancel.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{wmel3.png}
	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs. $\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
	\label{fig:doubsive}
\end{figure}

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{cob.png}
	\caption{
		(a,c) Singly Resonant SIVE (SR-SIVE) and (b,d) Doubly Resonant SIVE (DR-SIVE) response of CNCbl using the $-\vec{k}_1 + 2\vec{k}_2$ and $\vec{k}_1 + 2\vec{k}_2$ phasematching geometries, respectively.
		Here, $\omega_2 = 8000$ cm$^{-1}$.
		$\omega_1$ is stepped in 10 $^{-1}$ intervals.
		The spectra are smoothed and power-normalized for frequency dependent power fluctuations during the scan.
		Gray pixels indicate spectral noise.
		The blue trace in (a), (b) corresponds to the spectrum at $\tau_{12}$ = 0 in (c,d), respectively.
		The red trace is an FT-IR spectrum of CNCbl, sourced from NIST. 
		All spectra are normalized to their most intense feature on $\omega \in [1300, 1700]$ cm$^{-1}$.}
	\label{fig:cobsive}
\end{figure*}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{corr_contour.png}
	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
	\label{fig:contours}
\end{figure}
